Figures to insert in text

### 2018-04-03 kanerva-answer.tex
going very slow... theorem 2...

This is an important observation. A hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes' to write on its own corresponding bit-address more than it likes the opposite; as each hard-location has a say in its own area --- and nowhere else.

Let $x$ and $y$ be random bitstrings and $n$ be the number of dimensions in the memory; let $x_i$ and $y_i$ be the $i$-th bit of $x$ and $y$, respectively; and $d(x, y)$ be the Hamming distance. Whilst the probability of a shared bit-value between same dimension-bits in two random addresses is $1/2$, an address only activates hard-locations close to it.

So what is the probability of shared bit-values given that we know the access radius $r$ between the address and a hard-location?
\bigskip

\begin{theorem}
%\emph{(Lagrange's Theorem)}
\label{T1}
$P(x_i = y_i | d(x, y) \le r) = \dfrac{\sum_{k=0}^{r} \binom{n-1}{k}}{\sum_{k=0}^{r} \binom{n}{k}}$
\end{theorem}

\begin{proof}
    Applying the law of total probability to the left-hand expression we obtain

@@

This equation is valid for both ``x at x'' (autoassociative memory) and ``random at x'' (heteroassociative memory). When $n=1,000$ and $r=451$, $P(x_i = y_i | d(x, y) \le r) = p = 0.552905498137$.

Hence, let $Z$ be the number of activated hard location with the same bit as the reading address, then: $Z = \sum_{i=1}^{h} X_i$, where $\mathbf{E}[h] = h$, $\mathbf{V}[h] = H p_1 (1-p_1)$, $p_1 = 2^{-n} \sum_{k=0}^{r} \binom{n}{k}$, and $X_i \sim \text{Bernoulli}(p)$. By the central limit theorem, $Z$ is normally distributed.

@@

  \caption{The histogram was obtained through simulation. The red curve is the theoretical normal distribution.}
  \label{fig:sdm-same-bit-histogram}
\end{figure}

@@

\begin{align}
\left[ \text{cnt}_i | \text{addr}_i=1 \right] &\sim \mathcal{N}(\mu_2 = (2p-1) \theta, \sigma_2^2 = 4 \sigma_1^2) \\
\left[ \text{cnt}_i | \text{addr}_i=0 \right] &\sim \mathcal{N}(\mu_2 = -(2p-1) \theta, \sigma_2^2 = 4 \sigma_1^2)
\end{align}

@@

  \caption{The value of the counters after $s=10,000$ writes shows the autocorrelation in the counters in autoassociative memories (``x at x''). The histogram was obtained through simulation. The red curve is the theoretical normal distribution.}
  \label{fig:sdm-corr-counters}
\end{figure}

>>>>

This is an important observation. A hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes' to write on its own corresponding bit-address value more than it likes the opposite; as each hard-location has a say in its own area --- and nowhere else.

Let $x$ and $y$ be random bitstrings and $n$ be the number of dimensions in the memory; let $x_i$ and $y_i$ be the $i$-th bit of $x$ and $y$, respectively; and $d(x, y)$ be the Hamming distance. Whilst the probability of a shared bit-value between same dimension-bits in two random addresses is $1/2$, an address only activates hard-locations close to it.  Let us call these shared bitvalues a \emph{bitmatch in dimension $i$}.

So, what is the probability of bitmatches given that we know the access radius $r$ between the address and a hard-location?
\bigskip

\begin{theorem}
\emph{Each dimension has a small pull bias, which can be measured by}
\label{T1}
$P(x_i = y_i | d(x, y) \le r) = \dfrac{\sum_{k=0}^{r} \binom{n-1}{k}}{\sum_{k=0}^{r} \binom{n}{k}}.$
\end{theorem}

\begin{proof}
    The left-hand expression $P(x_i = y_i | d(x, y) \le r)$ computes the probability of a bitmatch in $i$, given that we know that $x$ and $y$ are in the access radius defined by $r$, i.e., $d(x, y)\le r$.

    Applying the law of total probability to the left-hand expression we obtain

@@

Theorem \ref{T1} is valid for both ``x at x'' (autoassociative memory) and ``random at x'' (heteroassociative memory). When $n=1,000$ and $r=451$, $P(x_i = y_i | d(x, y) \le r) = p = 0.552905498137$.  Each bit of a hard location does indeed have a small pull bias.  What is meant by this is that each particular dimension has a small preference toward positive values if its address bit is set to 1, and negative values otherwise.

So far we have looked only at a single dimension.  Let us think about how the entire bitstring is affected by this result.

\begin{theorem}
\emph{Given a reading address $x$ and a dimension $i$, the number of activated hard-locations with bitmatches at $i$ follows a normal distribution with }
\label{T2}
$\mathbf{E}[Z] = ph$ and $\mathbf{V}[Z] = hp(1-p) + p^2 H p_1 (1-p_1)$.

\end{theorem}

Let $Z$ be the number of activated hard locations with the same bit as the reading address:

$Z = \sum_{i=1}^{h} X_i$,

where $\mathbf{E}[h] = h$, \\
$\mathbf{V}[h] = H p_1 (1-p_1)$, \\
$p_1 = 2^{-n} \sum_{k=0}^{r} \binom{n}{k}$, and \\
$X_i \sim \text{Bernoulli}(p)$. \\

By the central limit theorem, $Z$ is normally distributed.

@@

  \caption{The histogram was obtained through simulation. The red curve is the theoretical normal distribution found in \ref{T2}.}
  \label{fig:sdm-same-bit-histogram}
\end{figure}

@@

\begin{align}
\left[ \text{cnt}_i | \text{addr}_i=1 \right] &\sim \mathcal{N}(\mu_2 = (2p-1) \theta, \sigma_2^2 = 4 \sigma_1^2)\label{cntaddr1} \\
\left[ \text{cnt}_i | \text{addr}_i=0 \right] &\sim \mathcal{N}(\mu_2 = -(2p-1) \theta, \sigma_2^2 = 4 \sigma_1^2)\label{cntaddr0}
\end{align}

@@

  \caption{The value of the counters after $s=10,000$ writes shows the autocorrelation in the counters in autoassociative memories (``x at x''). The histogram was obtained through simulation. The red curve is the theoretical normal distribution found in (\ref{cntaddr1}) and (\ref{cntaddr0}).}
  \label{fig:sdm-corr-counters}
\end{figure}
